Ensemble Methods for Robust Feature Selection

### 2016-07-18 paper/paper.tex
added lasso to paper
changed names in paper

\author{\name Marina Meil\u{a} \email mmp@stat.washington.edu \\
       \addr Department of Statistics\\
       University of Washington\\
       Seattle, WA 98195-4322, USA
       \AND
       \name Michael I.\ Jordan \email jordan@cs.berkeley.edu \\
       \addr Division of Computer Science and Department of Statistics\\
       University of California\\
       Berkeley, CA 94720-1776, USA}

\editor{Leslie Pack Kaelbling}

@@

The third feature selection method we used was a recursive feature elmination in combination with SVM \citep{guyon2002gene}.
Recursive feature elimination fits a SVM and ranks the feature according to their importance in the model,
based on the weight vector of the hyperplane.
More precisely after obtaining the solution for the primal problem of the SVM in equation \ref{eq:svm_primal},
the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
\begin{alignat}{-1}
     \min_{w,b}  & \quad \frac12\|w\|^2 + C\sum_{i=1}^m \xi_i & & & \label{eq:svm_primal} \\ 
   \text{s.\,t.} & \quad y^{(i)} (w^Tx^{i} + b) & \quad \geq & \quad 1 -\xi_i &&
                   \quad \forall \, i = 1, \ldots, m \nonumber \\
                 & \quad \xi_i                  & \quad \geq & \quad 0 &&
                   \quad \forall \, i = 1, \ldots, m \nonumber 
\end{alignat}

@@

@@

\appendix
%\section*{Appendix A.}
%\label{app:some appendix}

>>>>

\author{\name Benjamin Rapier \u{a} \email benjamin.rabier@campus.tu-berlin.de \\
       \addr Neural Information Processing Group\\
       Technical University Berlin\\
       10623 Berlin, Germany}

       \AND
       \name Alexander Goscinski \email a.goscinski@mail.tu-berlin.de \\
       \addr Neural Information Processing Group\\
       Technical University Berlin\\
       10623 Berlin, Germany}

\editor{No Editor}

@@

The third feature selection method we used was a recursive feature elmination in combination with SVM \citep{guyon2002gene}.
Recursive feature elimination fits a SVM and ranks the feature according to their importance in the model,
based on the weight vector of the hyperplane.
More precisely after obtaining the solution for the primal problem of the SVM in equation \ref{eq:svm_primal},
the ranking coefficients $c_i$ for the features are then calculated by squaring the weights $c_i = w_i^2$.
\begin{alignat}{-1}
     \min_{w,b}  & \quad \frac12\|w\|^2 + C\sum_{i=1}^m \xi_i & & & \label{eq:svm_primal} \\ 
   \text{s.\,t.} & \quad y^{(i)} (w^Tx^{(i)} + b) & \quad \geq & \quad 1 -\xi_i &&
                   \quad \forall \, i = 1, \ldots, m \nonumber \\
                 & \quad \xi_i                  & \quad \geq & \quad 0 &&
                   \quad \forall \, i = 1, \ldots, m \nonumber 
\end{alignat}

@@

A form of Lasso

\begin{equation}
  \min_w \quad \frac1{2 \, \textrm{\#features}} \, \|y - Xw\|^2_2 + \alpha \, \|w\|_1
\end{equation}

@@

\appendix
\section*{Appendix A.}
For the feature selection methods SU and RELIEF e used the scikit-feature library from \cite{Li-etal16}.
\label{app:some appendix}
